Deciding to Disclose

### 2015-01-07 Model.tex
Grayscale friendliness, spelling

According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, follwed by subsequent action if a concern is raised is at the discretion of the midwife. This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team. On alcohol consumption, policy regarding how to determine the level of consumption is generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE. This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.

@@

Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level. Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

@@

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
\vskip
\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
\caption{Influence diagrams, showing the game broken into two decision problems}

@@

%Might belong in a more methody bit? Read some stuff to check..
To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}; and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).

@@

\begin{table}
\center
\subfloat[Social cost, \(X_{s}\), for women\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Medium & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Low & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

@@

\subfloat[Health outcome, \(X_{h}\), for women and midwives\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Referral cost, \(X_{c}\), for midwife\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

@@

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-ouput characteristics.

@@

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogenous beliefs about  women and assume to some extent that they are honest.
Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible for their type at least once, with exactly \(k\) encounters overall.

@@

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is clearly worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

@@

where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
psuedo-count of prior observations for a pair \(i\).

@@

\begin{equation}
P(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
\end{equation}

Where \(n_{j}\) is simply the count of occurrences of pair \(j\), so
that the belief that a signal \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.
As before, midwives follow a similar pattern but per signal.

Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m})
\end{equation}

where $X$ is the set of payoffs the agent has observed to follow $s$.

@@

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w})
\end{equation}

@@

Midwives reasoning centers on determining the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i, \theta_{m})p(i | s_{w})
\end{equation}

@@

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate more than two `prospects'.\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains and losses -

\begin{eqnarray}
w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\\
w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}
\end{eqnarray}

Where $p$ is the unweighted probability, and $\gamma$ and $\delta$
are the weights for gain and loss probabilities respectively. Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}) & \text{if}\, u_{i}>0\\
0 & \text{if}\, u_{i}=0\\
\lambda g(u_{i}) & \text{if}\, x<0
\end{cases}
\end{equation}

@@

\begin{equation}
f(u_{i})=\begin{cases}
u_{i}^{\alpha} & \text{if}\,\alpha>0\\
\ln(u_{i}) & \text{if}\,\alpha=0\\
1-(1+u_{i})^{\alpha} & \text{if}\,\alpha<0
\end{cases}
\end{equation}
\begin{equation}
g(u_{i})=\begin{cases}
-(-u_{i})^{\beta} & \text{if}\,\beta>0\\
-\ln(-u_{i}) & \text{if}\,\beta=0\\
(1-u_{i})^{\beta}-1 & \text{if}\,\beta<0
\end{cases}
\end{equation}

@@

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relys on a belief structure relating actions directly to rewards which is essentially model free. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

>>>>

According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife. This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team. On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE. This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.

@@

Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level. Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

@@

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
\vskip
\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

@@

%Might belong in a more methody bit? Read some stuff to check..
To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives. Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, with $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife. Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.

@@

\begin{table}
\center
\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Moderate & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Non & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

@@

\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

@@

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

@@

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
Women are heterogeneous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible for their type at least once, with exactly \(k\) encounters overall.

@@

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

@@

where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
pseudo-count of prior observations for a pair \(i\).

@@

\begin{equation}
p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
\end{equation}

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
that the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
\end{equation}

where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.

@@

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
\end{equation}

@@

Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

@@

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate more than two `prospects'.\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

\begin{align}
w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
\end{align}

where $p$ is the unweighted probability, and $\gamma$ and $\delta$
are the weights for gain and loss probabilities respectively. Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}),& \text{if}\, u_{i}>0\\
0,& \text{if}\, u_{i}=0\\
\lambda g(u_{i}),& \text{if}\, x<0
\end{cases},
\end{equation}

@@

\begin{equation}
f(u_{i})=\begin{cases}
u_{i}^{\alpha},& \text{if}\,\alpha>0\\
\ln(u_{i}),& \text{if}\,\alpha=0\\
1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
\end{cases}
\end{equation}
\begin{equation}
g(u_{i})=\begin{cases}
-(-u_{i})^{\beta},& \text{if}\,\beta>0\\
-\ln(-u_{i}),& \text{if}\,\beta=0\\
(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
\end{cases},
\end{equation}

@@

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

### 2015-01-07 Results.tex
Grayscale friendliness, spelling

\begin{figure}[H]
\includegraphics[width=119mm]{figures/ref_plot}
\caption{Average fraction of population referred after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:qt_trends}}
\end{figure}

@@

Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), and the associated increase in false positives. This arises because of the lack of homophilly in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal. The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.

The relationship is not, however, entirely straighforward, in that increasing information sharing leads to greater variance between runs. A linear model was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.

@@

Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. Also of interest is the large region of instability that can be discerned for the Bayesian rule under modest probability of information sharing and higher weights. This suggests that, perhaps unsurprisingly, that what information is shared is significant to outcomes.

>>>>

\begin{figure}[H]
\includegraphics[width=119mm]{figures/ref_plot}
\caption{Average fraction of population referred after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:referrals}}
\end{figure}

@@

Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), and the associated increase in false positives. This arises because of the lack of homophily in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal. The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.

The relationship is not, however, entirely straightforward, in that increasing information sharing leads to greater variance between runs. A linear model was used to predict the between-runs interquartile range of the average signal sent by moderate drinkers. The predictors used were decision rule, and level of information sharing, together with the interaction between the two. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.

@@

Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. This suggests that, perhaps unsurprisingly, that what information is shared is significant to outcomes.
